---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rosalindR

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
"[![License: MIT](https://img.shields.io/badge/license-MIT-blue.svg)](https://cran.r-project.org/web/licenses/MIT)"
<!-- badges: end -->

The goal of rosalindR is to offer an alternative platform to [Rosalind](http://rosalind.info/problems/locations/), a website aimed at providing students with bioinformatics coding challenges. In R, students can tackle these problems by being offered a .yaml file with questions and solutions. Open source conributors can further add more problems of Rosalind to this platform.

## Installation

As `rosalindR` is not on CRAN, you can install the development version of rosalindR from [GitHub](https://github.com/) through:

```{r install package}
# install.packages("devtools")
# install.packages('pkgdown')
# install.packages('tools')
# install.packages('badger')
devtools::install_github("zhemingfan/rosalindR")
```

## Example

This is a basic example which shows you how to write a YAML file. First we can load the package.

```{r load package}
library(rosalindR)
```

Then we can use the `create_question()` function to write a file. The function will output the filepath, which can be used for the future tasks.
```{r create function}
rosalindR::create_question("Name_of_package","~/.","AuthorName")
```

## Development

Overall, the initial configuration of this package was developed using the folllowing lines of code: 
```r_development
# Create package
usethis::create_package()

# Make a R script containing key function
usethis::use_r() #Specifically usethis::use_r("create_question)

# Load a package
devtools::load_all()

# Add a license
usethis::use_mit_license("Jeremy Fan")

# Install the package and restart R (alternatively, do install and restart in right hand drop down menu to access the functions in this package)
devtools::install()

# Create tests for package and test them
usethis::use_testthat()
usethis::use_test("create_question")

# Indicates dependencies
usethis::use_package("tools")

# Editing the README
usethis::use_readme_rmd()

# Build all vignettes
devtools::build_vignettes()
devtools::use_vignette('yaml_configuration')

# Add a code of conduct
usethis::use_code_of_conduct()

# Make a package website
usethis::use_pkgdown()
pkgdown::build_site()

# Activate with GitHub Pages
usethis::use_github_action("pkgdown")

# Add to the Changelog
usethis::use_news_md()

# Add a badge
usethis::use_lifecycle_badge("Experimental")

# Render the README
devtools::build_readme()

# Check the final output
devtools::check()
```

Github interaction was done through the command line through simple add, commit, and push commands. Debugging was done through `devtools::check()`. Everytime roxygen description of function was changed, `devtools::document()` was ran to update files in the `man` folder. Testing of a package through time was done through `devtools::test()`. 

## Manual work 

More work was to determine the badge license through the `badger::badge_license()` command. Function was written using existing R knowledge, and unit testing done with with own knowledge.
